---
title: "Survey Analysis"
format:
  html:
    code-fold: true
    code-summary: "Code"
---

```{r setup, include=FALSE}
library(ggplot2)
library(forcats) # for data
library(lubridate) # for dates
library(conflicted) # for managing namespace conflicts (functions with the same name)
conflicts_prefer(dplyr::select)
conflicts_prefer(dplyr::filter)
library(see)
library(parameters)
library(tibble)
library(dplyr)
library(lubridate)
library(forcats)
library(knitr)
library(kableExtra)
library(readr)

```


```{r datatables}
# Create data tables

# Create Codebook
codebook <- tibble(
  variable_name = c(
    "gender", "age", "annual_income", "employment_status", 
    "relationship_status", "loneliness_frequency", "group_calls", 
    "video_call_frequency", "social_media_platform", "paid_online_services", 
    "motivation_online_community", "platform_preference", "real_name_usage", 
    "subscription_payments", "sharing_comfort", "daily_meaningful_contacts", 
    "friend_count"
  ),
  question = c(
    "What is your gender?",
    "What is your age?",
    "What is your annual income?",
    "What is your employment status?",
    "What is your relationship status?",
    "How often do you feel lonely or isolated?",
    "Have you ever participated in group calls or support groups online?",
    "How often do you communicate with friends or family through video calls?",
    "Which social media platforms do you use most frequently?",
    "Do you subscribe to any paid online communities or services?",
    "What motivates you to join a new online community?",
    "What do you look for when choosing a platform for social interaction?",
    "How often do you use your real name on online services/platforms?",
    "How many subscription-based payments are you actively using right now?",
    "How comfortable are you sharing personal experiences in an online setting?",
    "How many people do you come into meaningful contact with on a daily basis?",
    "How many people could you call your friends?"
  )
)


set.seed(123)
data <- tibble(
  gender = sample(c("Female", "Male"), 100, replace = TRUE),
  age = sample(26:46, 100, replace = TRUE),  # Skewed age distribution
  annual_income = sample(c("0-15000 €", "15000-25000 €", "25000-35000 €", "35000-45000 €", "45000+ €"), 100, replace = TRUE),
  employment_status = sample(c("Unemployed", "Part-time", "Full-time", "Freelancer"), 100, replace = TRUE),
  relationship_status = sample(c("Single", "In a relationship", "Married", "Divorced"), 100, replace = TRUE),
  loneliness_frequency = sample(c("Never", "Rarely", "Sometimes", "Often", "Always"), 100, replace = TRUE),
  group_calls = sample(c("Yes", "No"), 100, replace = TRUE),
  video_call_frequency = sample(c("Never", "Rarely", "Sometimes", "Often", "Always"), 100, replace = TRUE),
  social_media_platform = sample(c("Instagram", "TikTok", "Facebook", "Twitter"), 100, replace = TRUE),
  paid_online_services = sample(c("Yes", "No"), 100, replace = TRUE),
  motivation_online_community = sample(c("Learning new skills", "Meeting new people", "Support for personal issues", "Entertainment"), 100, replace = TRUE),
  platform_preference = sample(c("Ease of use", "Privacy features", "Community guidelines", "Content quality"), 100, replace = TRUE),
  real_name_usage = sample(c("Never", "Rarely", "Sometimes", "Often", "Always"), 100, replace = TRUE),
  subscription_payments = sample(c("None", "1-3", "4-5", "6 or more"), 100, replace = TRUE),
  sharing_comfort = sample(c("Very uncomfortable", "Uncomfortable", "Neutral", "Comfortable", "Very comfortable"), 100, replace = TRUE),
  daily_meaningful_contacts = sample(c("None", "1-5", "6-10", "11-20", "20 and more"), 100, replace = TRUE),
  friend_count = sample(c("None", "1-3", "4-6", "6-8", "8 and more"), 100, replace = TRUE)
)

adjust_loneliness <- function(employment_status, relationship_status, friend_count, age) {
  if (employment_status == "Full-time") {
    return(sample(c("Never", "Rarely", "Sometimes", "Often", "Always"), 1, prob = c(0.05, 0.10, 0.25, 0.30, 0.30)))  
  } else if (relationship_status %in% c("In a relationship", "Married")) {
    return(sample(c("Never", "Rarely", "Sometimes", "Often", "Always"), 1, prob = c(0.30, 0.30, 0.25, 0.10, 0.05)))  
  } else if (friend_count %in% c("6-8", "8 and more")) {
    return(sample(c("Never", "Rarely", "Sometimes", "Often", "Always"), 1, prob = c(0.40, 0.30, 0.20, 0.05, 0.05)))  
  } else if (age >= 30 & age <= 39) {
    return(sample(c("Never", "Rarely", "Sometimes", "Often", "Always"), 1, prob = c(0.05, 0.15, 0.30, 0.30, 0.20)))  
  } else {
    return(sample(c("Never", "Rarely", "Sometimes", "Often", "Always"), 1, prob = c(0.15, 0.25, 0.30, 0.20, 0.10)))  
  }
}

# Function to assign motivation for online community participation
adjust_motivation <- function() {
  return(sample(c("Learning new skills", "Meeting new people", "Support for personal issues", "Entertainment"), 1,
                prob = c(0.15, 0.15, 0.50, 0.20)))  # More people joining for support
}

# Function to adjust sharing comfort level
adjust_sharing_comfort <- function() {
  return(sample(c("Very uncomfortable", "Uncomfortable", "Neutral", "Comfortable", "Very comfortable"), 1,
                prob = c(0.05, 0.10, 0.20, 0.35, 0.30)))  # More people feel comfortable sharing
}

# Function to adjust real name usage based on subscription
adjust_real_name_usage <- function(paid_online_services) {
  if (paid_online_services == "Yes") {
    return(sample(c("Never", "Rarely", "Sometimes", "Often", "Always"), 1, prob = c(0.05, 0.10, 0.25, 0.30, 0.30)))  
  } else {
    return(sample(c("Never", "Rarely", "Sometimes", "Often", "Always"), 1, prob = c(0.15, 0.20, 0.30, 0.20, 0.15)))  
  }
}

# Apply probability adjustments
data <- data %>%
  rowwise() %>%
  mutate(
    loneliness_frequency = adjust_loneliness(employment_status, relationship_status, friend_count, age),
    motivation_online_community = adjust_motivation(),
    sharing_comfort = adjust_sharing_comfort(),
    real_name_usage = adjust_real_name_usage(paid_online_services)
  )
```

# Questionnaire

The table below provides a codebook for the survey questionnaire, listing variable names and the corresponding questions:

```{r codebook}
codebook |>
  kable(caption = "Survey Questionnaire Codebook") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

# Data Overview

The survey dataset contains responses to questions on demographic and behavioral characteristics. Here is a preview of the first few rows:

```{r data-preview}
data |> 
  head() |> 
  kable(caption = "Survey Data Preview") |> 
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

#  Statistics


## Factors to Numeric
```{r data-edit}
data <- data %>%
  mutate(
    loneliness_frequency = as.numeric(factor(loneliness_frequency, levels = c("Never", "Rarely", "Sometimes", "Often", "Always"), ordered = TRUE)),
    employment_status = factor(employment_status),
    relationship_status = factor(relationship_status),
    group_calls = factor(group_calls, levels = c("No", "Yes"), ordered = TRUE),
    sharing_comfort = as.numeric(factor(sharing_comfort, levels = c("Very uncomfortable", "Uncomfortable", "Neutral", "Comfortable", "Very comfortable"), ordered = TRUE)),
    real_name_usage = as.numeric(factor(real_name_usage, levels = c("Never", "Rarely", "Sometimes", "Often", "Always"), ordered = TRUE)),
    friend_count = as.numeric(factor(friend_count, levels = c("None", "1-3", "4-6", "6-8", "8 and more"), ordered = TRUE)),
    daily_meaningful_contacts = as.numeric(factor(daily_meaningful_contacts, levels = c("None", "1-5", "6-10", "11-20", "20 and more"), ordered = TRUE))
  )
```


## Age Distribution

```{r age-plot}
# Age distribution
data %>%
  mutate(age_group = cut(age, breaks = seq(26, 46, by = 10), include.lowest = TRUE)) %>%
  group_by(age_group) %>%
  summarize(mean_loneliness = mean(loneliness_frequency, na.rm = TRUE)) %>%
  ggplot(aes(x = age_group, y = mean_loneliness, fill = age_group)) +
  geom_bar(stat = "identity", alpha = 0.8) +
  labs(
    title = "Mean Loneliness Frequency by Age Group",
    x = "Age Group",
    y = "Mean Loneliness Frequency",
    fill = "Age Group"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Relationship
```{r relationship-plot}
ggplot(data, aes(x = relationship_status, y = loneliness_frequency, fill = relationship_status)) +
  geom_boxplot() +
  labs(title = "Relationship Status vs. Loneliness Frequency", x = "Relationship Status", y = "Loneliness Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Income
```{r income-plot}
ggplot(data, aes(x = annual_income, y = daily_meaningful_contacts, fill = annual_income)) +
  geom_boxplot() +
  labs(title = "Annual Income vs. Daily Meaningful Contacts", x = "Annual Income", y = "Number of Meaningful Contacts") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Friend
```{r friend-plot}
data %>%
  group_by(friend_count) %>%
  summarize(mean_loneliness = mean(loneliness_frequency, na.rm = TRUE)) %>%
  ggplot(aes(x = friend_count, y = mean_loneliness, group = 1)) +
  geom_line(color = "blue", size = 1) +
  geom_point(color = "red", size = 2) +
  labs(
    title = "Mean Loneliness Frequency by Friend Count",
    x = "Number of Friends",
    y = "Mean Loneliness Frequency"
  ) +
  theme_minimal()
```








